\section*{参考文献}
\begin{enumerate}[label={[\arabic*]},leftmargin=3em,labelsep=.75em,itemsep=.5em,topsep=.3em,parsep=0pt]
\item Bernhard Haeupler, Richard Hladík, Václav Rozhoň, Robert E. Tarjan, and Jakub Tětek. 2025. \emph{Universal Optimality of Dijkstra via Beyond-Worst-Case Heaps}. arXiv:2311.11793v4. Substantially rewritten and improved version of the FOCS 2024 paper.
\item Edsger W. Dijkstra. 1959. \emph{A note on two problems in connexion with graphs}. Numerische Mathematik.
\item Michael L. Fredman and Robert E. Tarjan. 1987. \emph{Fibonacci heaps and their uses in improved network optimization algorithms}. Journal of the ACM.
\item Michael L. Fredman, Robert Sedgewick, Daniel D. Sleator, and Robert E. Tarjan. 1986. \emph{The Pairing Heap: A New Form of Self-Adjusting Heap}. Algorithmica.
\item Bernhard Haeupler, Siddhartha Sen, and Robert E. Tarjan. 2011. \emph{Rank-Pairing Heaps}. SIAM Journal on Computing.
\item Thomas D. Hansen, Haim Kaplan, Robert E. Tarjan, and Uri Zwick. 2017. \emph{Hollow Heaps}. ACM Transactions on Algorithms.
\item Amr Elmasry. 2006. \emph{A Priority Queue with the Working-Set Property}. International Journal of Foundations of Computer Science.
\item Amr Elmasry, Arash Farzan, and John Iacono. 2012. \emph{A priority queue with the time-finger property}. Journal of Discrete Algorithms.
\item Scott Huddleston and Kurt Mehlhorn. 1982. \emph{A New Data Structure for Representing Sorted Lists}. Acta Informatica 17, 157-184. doi:10.1007/BF00288968.
\item Tim Roughgarden. 2020. \emph{Beyond the Worst-Case Analysis of Algorithms}. Cambridge University Press.
\item Bernhard Haeupler, David Wajc, and Goran Zuzic. 2021. \emph{Universally-Optimal Distributed Algorithms for Known Topologies}. STOC 2021.
\item Bernhard Haeupler, Richard Hladik, John Iacono, Vaclav Rozhon, Robert E. Tarjan, and Jakub Tetek. 2025. \emph{Fast and Simple Sorting Using Partial Information}. SODA 2025.
\item Ran Duan, Jiayi Mao, Xiao Mao, Xinkai Shu, and Longhui Yin. 2025. \emph{Breaking the Sorting Barrier for Directed Single-Source Shortest Paths}. arXiv:2504.17033.
\item Ivor van der Hoog, Eva Rotenberg, and Daniel Rutschmann. 2025. \emph{Simpler Universally Optimal Dijkstra}. ESA 2025, LIPIcs 351, 71:1-71:9. doi:10.4230/LIPIcs.ESA.2025.71. arXiv:2504.17327.
\item Bernhard Haeupler, Richard Hladik, Vaclav Rozhon, Robert E. Tarjan, and Jakub Tetek. 2025. \emph{Bidirectional Dijkstra's Algorithm is Instance-Optimal}. 8th SIAM Symposium on Simplicity in Algorithms (SOSA 2025), 202-215. doi:10.1137/1.9781611978315.15.
\item Sandeep Sen. 2025. \emph{Towards universally optimal sorting algorithms}. arXiv:2506.08261.
\item Benjamin Aram Berendsohn. 2026. \emph{Universally Optimal Decremental Tree Minima}. arXiv:2602.15977.
\item Mikkel Thorup. 2004. \emph{Integer Priority Queues with Decrease Key in Constant Time and the Single Source Shortest Paths Problem}. Journal of Computer and System Sciences 69(3), 330-353. doi:10.1016/j.jcss.2004.04.003.
\end{enumerate}
